Poker Chips, Earthquakes, and Computation

### 2014-10-11 finaldraft.tex
adding final draft
modified notations section

First, we formalize the board of poker chips. We consider the integer lattice $\mathbb{Z} \times \mathbb{Z}$ as the set of nodes, indexed by the corresponding coordinate. We made the two nodes have an edge between them if they are a distance of 1 apart.

\begin{definition} A board is a function $b: \mathbb{Z} \times \mathbb{Z} \to \mathbb{Z}_{\geq 0}$.
The input to this function correspond to the nodes and the output is the number of chips on that node. Let $\mathcal{B}$ denote the set of all boards.
\end{definition}

In order to keep our notation compact we let $n(i,j)$ be the set of neighbors of node $(i,j)$.
\begin{definition}
We define the function $n: \mathbb{Z} \times \mathbb{Z} \rightarrow \mathbb{Z}^2 \times \mathbb{Z}^2 \times \mathbb{Z}^2 \times \mathbb{Z}^2 $ as 
\begin{equation}
n(i,j) = \{ (i+1, j), (i-1, j), (i, j-1), (i, j+1) \}.
\end{equation}
\end{definition}

>>>>

First, we formalize the definition of a board. The board is an infinite grid graph with a nonnegative number of chips placed at each node
\begin{center}
\includegraphics[scale=0.5]{grid1.png}
\end{center}

We can coordinatize the grid graph by labeling it like the standard Cartesian grid, where we fix one node to be the origin $(0,0)$, and we index all other nodes by integer coordinates $(i,j)$. We will define the board as a function from the Cartesian grid to the nonnegative integers.

\begin{definition} We write boards as functions $b$ from $\mathbb{Z}^2 \to \mathbb{Z}_{\geq 0}$.
\end{definition}

This function maps node labels given as integer coordinates to chip stack sizes. For example, if a board $b$ has 15 chips at the node with coordinate $(5,4)$, then $b(5,4) = 15$.

\begin{definition} We define $n(i,j)$ to be the set of neighbors of node $(i,j)$
\begin{equation*}
n(i,j) = \{ (i+1, j), (i-1, j), (i, j-1), (i, j+1) \}.
\end{equation*}
\end{definition}
